---
title: "Luquillo LTER"
authors: Wylie Hampson, Allie Cole, Grace Lewin, Charles Hendrickson
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(lubridate)
library(janitor)
```

## Import the data

```{r}
# PRM Data set
prm_data <- read_csv("/courses/EDS214/team_basset_hound/data/RioMameyesPuenteRoto.csv", na = "-9999")

# BQ1 Data set
bq1_data <- read_csv("/courses/EDS214/team_basset_hound/data/QuebradaCuenca1-Bisley.csv", na = "-9999")

# BQ2 Data set
bq2_data <- read_csv("/courses/EDS214/team_basset_hound/data/QuebradaCuenca2-Bisley.csv", na = "-9999")

<<<<<<< HEAD
# BQ3 Data set
bq3_data <- read.csv("/courses/EDS214/team_basset_hound/data/QuebradaCuenca3-Bisley.csv", na = "-9999")
=======
```{r}
# Read in the data from EDI -- Luquillo LTER
q1_data <- read_csv("/courses/EDS214/team_basset_hound/data/QuebradaCuenca1-Bisley.csv", na = "-9999")

q1_data_subset <- q1_data %>% 
  clean_names()
>>>>>>> ce71008b609b272733d84fcfa0433e29bca9ad47
```

## Cleaning data

```{r}
#Checked the meta data to make sure units are good 
prm_subset <- prm_data %>% 
  clean_names() %>% 
  select(sample_date, sample_id, no3, k) %>% 
  mutate(sample_date = lubridate::mdy(sample_date))

bq1_subset <- bq1_data %>% 
  clean_names() %>% 
  select(sample_date, sample_id, no3, k) %>% 
  mutate(sample_date = mdy(sample_date))

bq2_subset <-  bq2_data %>% 
  clean_names() %>% 
  select(sample_date, sample_id, no3, k) %>% 
  mutate(sample_date = mdy_hm(sample_date))

bq3_subset <- bq3_data %>% 
  clean_names() %>% 
  select(sample_date, sample_id, no3, k) %>% 
  mutate(sample_date = mdy(sample_date))

```

## Join the separate data frames

```{r}
full_df <- full_join(prm_subset, bq1_subset) %>% 
  full_join(bq2_subset) %>% 
  full_join(bq3_subset)
```

## Plot the data

```{r}

<<<<<<< HEAD
=======
bq3_subset <- bq3_data %>% 
  select(Sample_ID, Sample_Date, NO3, K)

y = "taylor token check" 
>>>>>>> ce71008b609b272733d84fcfa0433e29bca9ad47
```


